---
title: "Dev notebook"
format: html
---


```{r}
devtools::load_all(".")
```


```{r}
data_train()
```

# Stackoverflow

How can I get a path to a file in my own package that works
1. in both the development as well as the usage context of the package
2. without hard-coding the package's name
3. (ideally) without depending on an contributed package

I know that stackovervlow doesn't like these "most elegant/best" type of questions, but I'm feeling bold 😉

I'm looking for something like what `testthat::test_path()` does

When creating a  `golem` app the package creates `app_sys()`

```{r}
app_sys <- function(...) {
  system.file(..., package = "dbt.def.mod.01")
}
```

That's cool, but I don't like the fact that you need to hard-code the package name.

Here's what I currently use

```{r}
pkg_file <- function(path) {
    pkgload:::shim_system.file(path,
        package = pkgload::pkg_name())
}
```

Supposing that `inst/app/some_config.yml` exists calling `pkg_file("app/some_config.yml")` would either give me 

```
"/Users/jankothyson/Code/dbt/dbt.def.data/inst/app/some_config.yml"
```

or 

```

```

# Targets

```{r}
targets::tar_make()
targets::tar_manifest()
targets::tar_list()
targets::tar_read(path_data_001_employee_fluctuation_train)
targets::tar_read(data_001_employee_fluctuation_train)
```

# Data

```{r}
load("data/data_001_employee_fluctuation_train.rda")
data  <- data_001_employee_fluctuation_train
```

# Crosswalk: encoding

Extract

```{r}
# library(magrittr)
cw_encodings <- data %>% cw_encoding_extract()
```

Expand

```{r}
cw_encodings %>% names()
cw_encoding_expanded <- cw_encodings[1] %>% cw_encoding_expand(encoding_prefill = "original")
cw_encoding_expanded <- cw_encodings["Attrition"] %>% cw_encoding_expand(encoding_prefill = "original")
```

```{r, eval = FALSE}
cw_encoding_expanded %>% tidyr::pivot_wider(names_from = "variable", values_from = "encoding_de_internal")
```

```{r}
library(janitor)
# Create a data frame with English encodings and German translations
translation_df <- data.frame(English = c("Hello", "Goodbye", "Thank you"),
                             German = c("Hallo", "Auf Wiedersehen", "Danke"))

# Create a data frame with the encoding column
df <- data.frame(Language = c("Hello", "Thank you", "Goodbye"))

# Join the data frames based on the Language column
df_merged <- merge(df, translation_df, by = "Language")

# Select the columns you want to keep in the merged data frame
df_translated <- df_merged[, c("Language", "German")]

# Rename the Language column to English
names(df_translated)[names(df_translated) == "Language"] <- "English"
```

```{r}
# Install and load the dplyr package
library(dplyr)

# Create a data frame with English encodings and German translations
translation_df <- data.frame(English = c("Hello", "Goodbye", "Thank you"),
                             German = c("Hallo", "Auf Wiedersehen", "Danke"))

# Create a data frame with the encoding column
df <- data.frame(Language = c("Hello", "Thank you", "Goodbye"))

# Join the data frames based on the Language column
df_translated <- left_join(df, translation_df, by = c("Language" = "English"))

# Select the columns you want to keep in the merged data frame
df_translated <- df_translated[, c("Language", "German")]

# Rename the Language column to English
names(df_translated)[names(df_translated) == "Language"] <- "English"
```

```{r}
# Function to translate an encoding from multiple languages to one language
translate_encoding <- function(df, encoding_col, translation_df, from_cols, to_col) {
  # Join the data frames based on the encoding column
  require(dplyr)
  df_translated <- left_join(df, translation_df, by = encoding_col)
  
  # Select the columns you want to keep in the joined data frame
  df_translated <- df_translated[, c(encoding_col, to_col)]
  
  # Rename the encoding column to the original encoding
  names(df_translated)[names(df_translated) == encoding_col] <- paste0(encoding_col, "_Original")
  
  return(df_translated)
}

# Example usage: Translate an encoding from three languages (English, French, and German) to Spanish
df <- data.frame(Language = c("Hello", "Thank you", "Goodbye", "Bonjour", "Danke", "Auf Wiedersehen"))
translation_df <- data.frame(English = c("Hello", "Goodbye", "Thank you"),
                             French = c("Bonjour", "Au revoir", "Merci"),
                             German = c("Hallo", "Auf Wiedersehen", "Danke"),
                             Spanish = c("Hola", "Adiós", "Gracias"))
df_translated <- translate_encoding(df, "Language", translation_df, c("English", "French", "German"), "Spanish")
```


```{r}
# Function to translate an encoding from multiple languages to one language
translate_encoding <- function(df, translation_df, col_by_left, col_by_right, col_to) {
  # Join the data frames based on the encoding column
  by <- c(col_by_right) %>% purrr::set_names(col_by_left)
  df_translated <- dplyr::left_join(
    df, 
    translation_df %>% dplyr::select(col_by_right, col_to), 
    by = by)
  
  # Select the columns you want to keep in the joined data frame
  df_translated <- df_translated[, c(col_by_right, col_to)]
  
  # # Rename the encoding column to the original encoding
  # names(df_translated)[names(df_translated) == encoding_col] <- paste0(encoding_col, "_Original")
  
  return(df_translated)
}

# Example usage: Translate an encoding from three languages (English, French, and German) to Spanish
df <- data.frame(value = c("Hello", "Thank you", "Goodbye", "Bonjour", "Danke", "Auf Wiedersehen"))
translation_df <- data.frame(encoding_en = c("Hello", "Goodbye", "Thank you"),
                             encoding_fr = c("Bonjour", "Au revoir", "Merci"),
                             encoding_de = c("Hallo", "Auf Wiedersehen", "Danke"),
                             encoding_es = c("Hola", "Adiós", "Gracias"))
df_translated <- translate_encoding(df, translation_df, col_by_left = "value", col_by_right = "encoding_en", col_to = "encoding_de")
```

```{r}
translation_df %>% write.csv("translation_df.csv", row.names = FALSE)
```

```{r}
```

Persist individual encoding

```{r}
cw_encodings_expanded <- cw_encodings %>% cw_encodings_expand()
cw_encodings_expanded %>% cw_encodings_persist(overwrite = TRUE) %>% sort()
```

Persit multiple encodings

```{r}

```


```{r}
.col <- "de"
"encoding_" %>%
            stringr::str_c(.col) %>%
            dplyr::sym()
```


```{r}
paths_cw_encoding <- cw_encoding %>% cw_encoding_persist() %>% sort()
```

# Crosswalk: rename column

```{r}
data %>%
  cw_encode_column(
      path_cw_encoding = paths_cw_encoding[1],
      vec_cast = FALSE
  )
```

# Crosswalk: rename columns

```{r}
data %>%
  cw_encode_columns(
      crosswalk_files = paths_cw_encoding[1:2],
      vec_cast = FALSE
  )
```


```{r}
usethis::use_data_raw("data_001_employee_fluctuation_train")
usethis::use_data
```
--------------------------------------------------------------------------------

# Google Cloud Translation API

```{r}
renv::install(c("googleAuthR", "googleCloudStorageR"))

# Load the googleAuthR and googleCloudStorageR packages
library(googleAuthR)
library(googleCloudStorageR)
library(httr)

# Set your API key
api_key <- "API_KEY"

# Set the source and target languages
source_language <- "en"
target_language <- "de"

# Set the text to translate
text <- "Hello"
text <- data %>% dplyr::count(EducationField) %>% dplyr::pull(EducationField)

response <- POST(
  "https://translation.googleapis.com/language/translate/v2",
  query = list(
    key = api_key,
    source = source_language,
    target = target_language,
    q = text[1:2],
    format = "text"
  )
)

# Parse the response as JSON
translation <- content(response, as = "parsed")

# Print the translated text
translation$data$translations[[1]]$translatedText
```


--------------------------------------------------------------------------------

# Backup

## Debugger

```{r}
foo
foo(1)
```



